\section{Integral Calculus}
Note, Riemann Integral was taught in this class.

\hyperref[measure_zero]{Measure Zero}


\subsection{Definitions}
\begin{description}
\item[rectangle (in $\bR^n$)] $Q = [a_1,b_1]\times[a_2,b_2]\times[a_n,b_n]$
\item[component interval of $Q$] $[a_i,b_i]$
\item[volume of $Q$] $v(Q) = (b_1-a_1)(b_2-a_2)\cdots(b_n-a_n)$
\item[partition] (of $[a, b]$) a finite collection of points of $[a,b]$ includes the points a, b
\item[partition] (of $Q$) n-tuple $(P_1, \ldots, P_n)$
\item[subinterval(determined by $P$)] \OMIT
\item[subrectangle(determined by $P$)] \OMIT
\item[mech of $P$] \OMIT
\item[refinement] \OMIT
\item[common refinement] \OMIT
\item[lower sum] $L(f, P)=\sum_R m_R(f)\cdot v(R)$\hfill\\
	where $m_R(f)=\inf\{f(x)|x\in R\}$
\item[upper sum] $U(f, P)=\sum_R M_R(f)\cdot v(R)$\hfill\\
	where $M_R(f)=\inf\{f(x)|x\in R\}$
\item[lower integral] $\underline{\int_Q}f=\sup_P\{L(f,P)\}$
\item[upper integral] $\overline{\int_Q}f=\inf_P\{L(f,P)\}$
\item[oscillation] \TODO
\item[rectifiable set] A bounded set $S\in\bR^n$ is rectifiable if the constant function 1 is integrable over $S$.
\extranote{S is rectifiable iff S is bounded and $\mathrm{Bd}S$ has measure zero}
\item[volume of a rectifiable set] $v(S)=\int_S 1$
\item[simple region] Let $C$ be a compact rectifiable in $R^{n-1}$;
	Let $\phi, \psi:C\to R$ be continuous function such that $\phi(x) \leq \psi(x)$ for $x\in C$.
	The subset $\{(x, t)|x\in C\wedge \phi(x) \leq t \leq \psi(x)\}$ is called a simple region in $R^n$.
\end{description}


\subsection{Ignored}
\begin{itemize}
\item Lemma 10.1: Munker p83.
\item Lemma 10.2: Munker p84.
\item Corollary 10.5: Munker p84.
\item Lemma 13.1: Munker p104.
\item Lemma 13.2: Munker p105.
\item Lemma 14.3: Munker p114. a simple region is compact and rectifiable.
\end{itemize}


\subsection{Riemann condition}
Given: \VAR{$Q$} a rectangle, \VAR{$f$} $: Q\to \bR$ a bounded function. Then
$\underline{\int_Q}f = \overline{\int_Q}f$ iff
given $\epsilon>0$ there exist a partion $P$ of $Q$ for which
$\forall\epsilon_{>0}\exists P[U(f, P)-L(f, P)\leq\epsilon]$

\extranote{Corollary/Theorem: every constant function is integrable.}


\subsection{Riemann-Lebesgue theorem}
A function on a compact interval [a, b] is Riemann integrable if and only if it is bounded and continuous almost everywhere (the set of its points of discontinuity has measure zero, in the sense of Lebesgue measure).
\WIKILINK{http://en.wikipedia.org/wiki/Riemann_integral\#Riemann_integral}
\MUNKERSREF{Munkers 11.2}

\subsection{Munkers 11.3}
Let $Q$ be a rectangle in $R^n$; let $f:Q \to \bR$; assume $f$ is integrable over $Q$.
\begin{itemize}
\item If $f$ vanishes except on a set of measure zero, then $\int_Q f=0$.
\item If $f$ is non-negative and if $\int_Q f=0$, then $f$ vanishes except on a set of measure zero.
\end{itemize}



\subsection{Fundamental theorem of Calculus}
\begin{itemize}
\item
	If $f$ is continuous on $[a, b]$, and if $F(X)=\int_a^x f$
	for $x\in[a,b]$, then $F'(x)$ exists and equals $f(x)$.
\item
	If $f$ is continious on $[a, b]$,
	and if $g$ is a function such that
	$g'(x)=f(x)$ for $x\in[a,b]$ then $\int_a^b f = g(b) - g(a)$
\end{itemize}


\subsection{Fubini's theorem}
Let $Q=A\times B$, where $A$ is a rectangle in $\bR^k$ and $B$ is a rectangle in $\bR^n$.
If f is bounded function and integrable over $Q$, then
$\underline{\int_{y\in B}} f(x,y)$ and $\overline{\int_{y\in B}} f(x,y)$ are integrable over $A$
and
\[\int_Q f = \int_{x\in A}\underline{\int_{y\in B}} f(x,y) = \int_{x\in A}\overline{\int_{y\in B}} f(x,y)\]

\subsubsection{For simple regions}
\TODO\MUNKERSREF{Munkers 14.4}

\[\int_S f = \int_{x\in C}\int_{t=\phi(x)}^{t=\psi(x)} f(x,t)\]


\subsection{Properties of integral}
\TODO\MUNKERSREF{Munkers 13.3}

\subsection{Properties of integral}
\TODO A set S is rectifiable iff S is bounded and has measure zero boundary.\MUNKERSREF{Munkers 14.1}

\subsection{Properties of rectifiable set}
\TODO\MUNKERSREF{Munkers 14.2}

